---
title: "Untitled"
author: "Brandon L. Kramer"
date: "10/28/2020"
output: html_document
---

https://supervised-ml-course.netlify.app/chapter1
https://juliasilge.com/blog/intro-tidymodels/


```{r setup, include=FALSE, warning = FALSE}
rm(list = ls())
library(tidyverse)
library(janitor)
library(tidymodels)
library(cowplot)
source("~/Documents/fantasy-basketball/funs/conv_to_points.R")
setwd("~/Documents/fantasy-basketball/data/nba_player_data/nba_player_season/")
nba_data <- read_rds("nba_stats_19902019_dedup.Rds")
gsd2_data <- read_rds("gsd2_draft_data.Rds")
forthcoming_salaries <- read_csv("../nba_player_salaries/nba_salaries_201920.csv")
selected_players <- read_csv("~/Documents/fantasy-basketball/data/nba_fantasy_data/gsd2_player_rankings - Drafted.csv") %>% mutate(player = tolower(player)) %>% clean_nba_names()
selected_players <- paste(c("\\b(?i)(zqx", na.omit(selected_players$player), "zqx)\\b"), collapse = "|")
fantrax_team_data <- read_csv("~/Documents/fantasy-basketball/data/nba_fantasy_data/Fantrax-Players-Gold Standard II.csv")

gsd2_data <- gsd2_data %>% 
  bbrhist_avgs_to_fppg() %>% 
  select(year, player, age, contains("fppg"), everything(), 
         -ld_fppg_bbr, -botb_fppg_bbr) %>%
  arrange(-gsd2_fppg_bbr) %>% 
  drop_na(salary, gsd2_fppg_bbr)

salaries <- forthcoming_salaries %>% 
  rename(player = Player) %>% 
  clean_nba_names()

gsd2_data_contracts <-gsd2_data %>% 
  filter(year == 2019) %>% 
  left_join(salaries, by = "player") %>% 
  select(-`Signed Using`, -Rk, -playerID, -Tm, -Guaranteed) %>%
  rename(y2020_21 = `y2020-21`, y2021_22 = `y2021-22`, y2022_23 = `y2022-23`, 
         y2023_24 = `y2023-24`, y2024_25 = `y2024-25`) %>% 
  mutate(y2020_21 = ifelse(y2020_21 > 30000001, 30000000, y2020_21),
         y2021_22 = ifelse(y2021_22 > 30000001, 30000000, y2021_22),
         y2022_23 = ifelse(y2022_23 > 30000001, 30000000, y2022_23),
         y2023_24 = ifelse(y2023_24 > 30000001, 30000000, y2023_24),
         y2024_25 = ifelse(y2024_25 > 30000001, 30000000, y2024_25))

gsd2_data_contracts %>% 
  mutate(y2020_21 = replace_na(y2020_21, 0),
         y2021_22 = ifelse(y2020_21 == 0, 0, y2021_22)) %>% 
  filter(is.na(y2021_22)) 

gsd2_data_contracts %>% 
  arrange(-gsd2_fppg_bbr) %>% 
  rename(fppg = gsd2_fppg_bbr) %>% 
  select(player, fppg, y2020_21, y2021_22, y2022_23, y2023_24,y2024_25) %>% 
  mutate(player = tolower(player)) %>% 
  filter(!grepl(selected_players, player) & 
           y2020_21 < 20000000 & fppg > 22) 
```

```{r}
proj_202122_cap <- 115000000
proj_202223_cap <- 118000000

model_data <- gsd2_data_contracts  %>% 
  mutate(y2020_21 = replace_na(y2020_21, 0),
         y2021_22 = replace_na(y2021_22, 0),
         y2022_23 = replace_na(y2022_23, 0),
         y2023_24 = replace_na(y2023_24, 0),
         y2024_25 = replace_na(y2024_25, 0)) %>% 
  mutate(proj_fppg = gsd2_fppg_bbr) %>% 
  
  mutate(y2022_23 = ifelse(y2020_21 == 0 & proj_fppg > 49.99, proj_202122_cap*0.275, 
                    ifelse(y2020_21 == 0 & proj_fppg > 44.99, proj_202122_cap*0.250, 
                    ifelse(y2020_21 == 0 & proj_fppg > 39.99, proj_202122_cap*0.225, 
                    ifelse(y2020_21 == 0 & proj_fppg > 34.99, proj_202122_cap*0.200, 
                    ifelse(y2020_21 == 0 & proj_fppg > 29.99, proj_202122_cap*0.175, 
                    ifelse(y2020_21 == 0 & proj_fppg > 24.99, proj_202122_cap*0.150, 
                    ifelse(y2020_21 == 0 & proj_fppg > 19.99, proj_202122_cap*0.100, 
                    ifelse(y2020_21 == 0 & proj_fppg > 14.99, proj_202122_cap*0.050, 
                    ifelse(y2020_21 == 0 & proj_fppg > 09.99, proj_202122_cap*0.025, 
                           y2023_24)))))))))) %>% 
  mutate(y2021_22 = ifelse(y2020_21 == 0 & proj_fppg > 49.99, proj_202122_cap*0.275, 
                    ifelse(y2020_21 == 0 & proj_fppg > 44.99, proj_202122_cap*0.250, 
                    ifelse(y2020_21 == 0 & proj_fppg > 39.99, proj_202122_cap*0.225, 
                    ifelse(y2020_21 == 0 & proj_fppg > 34.99, proj_202122_cap*0.200, 
                    ifelse(y2020_21 == 0 & proj_fppg > 29.99, proj_202122_cap*0.175, 
                    ifelse(y2020_21 == 0 & proj_fppg > 24.99, proj_202122_cap*0.150, 
                    ifelse(y2020_21 == 0 & proj_fppg > 19.99, proj_202122_cap*0.100, 
                    ifelse(y2020_21 == 0 & proj_fppg > 14.99, proj_202122_cap*0.050, 
                    ifelse(y2020_21 == 0 & proj_fppg > 09.99, proj_202122_cap*0.025, 
                           y2022_23)))))))))) %>% 
  mutate(y2020_21 = ifelse(y2020_21 == 0 & proj_fppg > 49.99, proj_202122_cap*0.275, 
                    ifelse(y2020_21 == 0 & proj_fppg > 44.99, proj_202122_cap*0.250, 
                    ifelse(y2020_21 == 0 & proj_fppg > 39.99, proj_202122_cap*0.225, 
                    ifelse(y2020_21 == 0 & proj_fppg > 34.99, proj_202122_cap*0.200, 
                    ifelse(y2020_21 == 0 & proj_fppg > 29.99, proj_202122_cap*0.175, 
                    ifelse(y2020_21 == 0 & proj_fppg > 24.99, proj_202122_cap*0.150, 
                    ifelse(y2020_21 == 0 & proj_fppg > 19.99, proj_202122_cap*0.100, 
                    ifelse(y2020_21 == 0 & proj_fppg > 14.99, proj_202122_cap*0.050, 
                    ifelse(y2020_21 == 0 & proj_fppg > 09.99, proj_202122_cap*0.025, 
                           y2020_21)))))))))) %>% 
  
  # resigns for next year assuming salary cap hike up to 115m and players produce the same 
  mutate(y2023_24 = ifelse(y2021_22 == 0 & proj_fppg > 49.99, proj_202122_cap*0.275, 
                    ifelse(y2021_22 == 0 & proj_fppg > 44.99, proj_202122_cap*0.250, 
                    ifelse(y2021_22 == 0 & proj_fppg > 39.99, proj_202122_cap*0.225, 
                    ifelse(y2021_22 == 0 & proj_fppg > 34.99, proj_202122_cap*0.200, 
                    ifelse(y2021_22 == 0 & proj_fppg > 29.99, proj_202122_cap*0.175, 
                    ifelse(y2021_22 == 0 & proj_fppg > 24.99, proj_202122_cap*0.150, 
                    ifelse(y2021_22 == 0 & proj_fppg > 19.99, proj_202122_cap*0.100, 
                    ifelse(y2021_22 == 0 & proj_fppg > 14.99, proj_202122_cap*0.050, 
                    ifelse(y2021_22 == 0 & proj_fppg > 09.99, proj_202122_cap*0.025, 
                           y2023_24)))))))))) %>% 
  mutate(y2022_23 = ifelse(y2021_22 == 0 & proj_fppg > 49.99, proj_202122_cap*0.275, 
                    ifelse(y2021_22 == 0 & proj_fppg > 44.99, proj_202122_cap*0.250, 
                    ifelse(y2021_22 == 0 & proj_fppg > 39.99, proj_202122_cap*0.225, 
                    ifelse(y2021_22 == 0 & proj_fppg > 34.99, proj_202122_cap*0.200, 
                    ifelse(y2021_22 == 0 & proj_fppg > 29.99, proj_202122_cap*0.175, 
                    ifelse(y2021_22 == 0 & proj_fppg > 24.99, proj_202122_cap*0.150, 
                    ifelse(y2021_22 == 0 & proj_fppg > 19.99, proj_202122_cap*0.100, 
                    ifelse(y2021_22 == 0 & proj_fppg > 14.99, proj_202122_cap*0.050, 
                    ifelse(y2021_22 == 0 & proj_fppg > 09.99, proj_202122_cap*0.025, 
                           y2022_23)))))))))) %>% 
  mutate(y2021_22 = ifelse(y2021_22 == 0 & proj_fppg > 49.99, proj_202122_cap*0.275, 
                    ifelse(y2021_22 == 0 & proj_fppg > 44.99, proj_202122_cap*0.250, 
                    ifelse(y2021_22 == 0 & proj_fppg > 39.99, proj_202122_cap*0.225, 
                    ifelse(y2021_22 == 0 & proj_fppg > 34.99, proj_202122_cap*0.200, 
                    ifelse(y2021_22 == 0 & proj_fppg > 29.99, proj_202122_cap*0.175, 
                    ifelse(y2021_22 == 0 & proj_fppg > 24.99, proj_202122_cap*0.150, 
                    ifelse(y2021_22 == 0 & proj_fppg > 19.99, proj_202122_cap*0.100, 
                    ifelse(y2021_22 == 0 & proj_fppg > 14.99, proj_202122_cap*0.050, 
                    ifelse(y2021_22 == 0 & proj_fppg > 09.99, proj_202122_cap*0.025, 
                           y2021_22)))))))))) %>% 
  # resigns for next year assuming salary cap hike up to 118m and players produce the same
  mutate(y2024_25 = ifelse(y2022_23 == 0 & proj_fppg > 49.99, proj_202223_cap*0.275, 
                    ifelse(y2022_23 == 0 & proj_fppg > 44.99, proj_202223_cap*0.250, 
                    ifelse(y2022_23 == 0 & proj_fppg > 39.99, proj_202223_cap*0.225, 
                    ifelse(y2022_23 == 0 & proj_fppg > 34.99, proj_202223_cap*0.200, 
                    ifelse(y2022_23 == 0 & proj_fppg > 29.99, proj_202223_cap*0.175, 
                    ifelse(y2022_23 == 0 & proj_fppg > 24.99, proj_202223_cap*0.150, 
                    ifelse(y2022_23 == 0 & proj_fppg > 19.99, proj_202223_cap*0.100, 
                    ifelse(y2022_23 == 0 & proj_fppg > 14.99, proj_202223_cap*0.050, 
                    ifelse(y2022_23 == 0 & proj_fppg > 09.99, proj_202223_cap*0.025, 
                           y2024_25)))))))))) %>% 
  mutate(y2023_24 = ifelse(y2022_23 == 0 & proj_fppg > 49.99, proj_202223_cap*0.275, 
                    ifelse(y2022_23 == 0 & proj_fppg > 44.99, proj_202223_cap*0.250, 
                    ifelse(y2022_23 == 0 & proj_fppg > 39.99, proj_202223_cap*0.225, 
                    ifelse(y2022_23 == 0 & proj_fppg > 34.99, proj_202223_cap*0.200, 
                    ifelse(y2022_23 == 0 & proj_fppg > 29.99, proj_202223_cap*0.175, 
                    ifelse(y2022_23 == 0 & proj_fppg > 24.99, proj_202223_cap*0.150, 
                    ifelse(y2022_23 == 0 & proj_fppg > 19.99, proj_202223_cap*0.100, 
                    ifelse(y2022_23 == 0 & proj_fppg > 14.99, proj_202223_cap*0.050, 
                    ifelse(y2022_23 == 0 & proj_fppg > 09.99, proj_202223_cap*0.025, 
                           y2023_24)))))))))) %>% 
  mutate(y2022_23 = ifelse(y2022_23 == 0 & proj_fppg > 49.99, proj_202223_cap*0.275, 
                    ifelse(y2022_23 == 0 & proj_fppg > 44.99, proj_202223_cap*0.250, 
                    ifelse(y2022_23 == 0 & proj_fppg > 39.99, proj_202223_cap*0.225, 
                    ifelse(y2022_23 == 0 & proj_fppg > 34.99, proj_202223_cap*0.200, 
                    ifelse(y2022_23 == 0 & proj_fppg > 29.99, proj_202223_cap*0.175, 
                    ifelse(y2022_23 == 0 & proj_fppg > 24.99, proj_202223_cap*0.150, 
                    ifelse(y2022_23 == 0 & proj_fppg > 19.99, proj_202223_cap*0.100, 
                    ifelse(y2022_23 == 0 & proj_fppg > 14.99, proj_202223_cap*0.050, 
                    ifelse(y2022_23 == 0 & proj_fppg > 09.99, proj_202223_cap*0.025, 
                           y2022_23)))))))))) %>%
  mutate(value1yr = round((gsd2_fppg_bbr / y2020_21) * 10000, 5), 
         value2yr = round((gsd2_fppg_bbr / y2020_21) + (gsd2_fppg_bbr / y2021_22)  * 10000, 5),
         value3yr = round((gsd2_fppg_bbr/y2020_21)+(gsd2_fppg_bbr/y2021_22)+
                            (gsd2_fppg_bbr/y2022_23)* 10000, 5),
         fppg = round(gsd2_fppg_bbr, 3)) %>% 
  select(player, fppg, value1yr, value2yr,  y2020_21, 
         y2021_22, y2022_23, y2023_24, y2024_25, everything()) %>% 
  arrange(-value1yr, age) %>% 
  mutate(player = tolower(player)) %>% 
  filter(!grepl(selected_players, player) & y2020_21 < 5000000 & position == "C"
         ) 
model_data
```
```{r}
model_data <- model_data %>% 
  #arrange(-gsd2_fppg_bbr) %>% 
  #rename(fppg = gsd2_fppg_bbr) %>% 
  select(player, fppg, y2020_21, y2021_22, y2022_23, y2023_24,y2024_25) %>% 
  mutate(player = tolower(player),
         y2020_21 = replace_na(y2020_21, 0)) %>% 
  filter(!grepl(selected_players, player)) 


fit <- lm(fppg ~ y2020_21, data=model_data) # fit the model
model_data$predicted_m1 <- predict(fit)   # Save the predicted values
model_data$residuals_m1 <- residuals(fit) # Save the residual values
#summary(fit)

model_data %>% 
  mutate(player = tolower(player)) %>% 
  filter(!grepl(selected_players, player)) %>%   
  ggplot(aes(x = y2020_21, y = fppg)) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +      
  geom_segment(aes(xend = y2020_21, yend = predicted_m1), alpha = .2) +   
  geom_point(aes(color = abs(residuals_m1), size = abs(residuals_m1))) +  
  scale_color_continuous(low = "#386890", high = "#40E0D0") +     
  geom_text(aes(label=player), size=3.5, hjust=0.5, 
            vjust=0, position=position_jitter(width=1, height=1)) +
  guides(color = FALSE, size = FALSE) +                             
  geom_point(aes(y = predicted_m1), shape = 1) + 
  scale_x_continuous(breaks = c(0, 5000000, 10000000, 15000000, 20000000, 25000000, 30000000, 35000000),
                     labels = c("0M", "5M", "10M", "15M", "20M", "25M", "30M", "35M")) +
  theme_minimal() + 
  xlab("Fantasy Points Per Game") + ylab("Annual Salary") +
  ggtitle("Visualizing Residuals as Fantasy Value (Baseline Model)") + 
  theme(plot.title = element_text(hjust = 0.5))
```
```{r}
model_data %>% 
  select(player, fppg, y2020_21, residuals_m1, predicted_m1) %>% 
  arrange(-residuals_m1) %>% 
  filter(y2020_21 != 0 )
```


#####################

```{r}
fantrax_team_data %>% 
  clean_names() %>% 
  filter(status != "(N/A)" & status != "FA") %>% 
  group_by(status) %>% 
  summarize(fp_g = sum(fp_g)) %>% 
  arrange(-fp_g)
```

```{r}
fantrax_team_data %>% 
  clean_names() %>% 
  filter(status != "(N/A)" & status != "FA") %>% 
  group_by(status) %>% 
  summarize(f_pts = sum(f_pts)) %>% 
  arrange(-f_pts)
```


```{r}
fit <- lm(gsd2_fppg_bbr ~ salary, data=gsd2_data) # fit the model
gsd2_data$predicted <- predict(fit)   # Save the predicted values
gsd2_data$residuals <- residuals(fit) # Save the residual values


tmp_data <- tmp_data %>% 
  select(-`Signed Using`, -Rk, -playerID, -Tm, -Guaranteed) %>% 
  mutate(`y2021-22` = replace_na(`y2021-22`, 0),
         `y2022-23` = replace_na(`y2022-23`, 0),
         `y2023-24` = replace_na(`y2023-24`, 0),
         `y2024-25` = replace_na(`y2024-25`, 0)) %>% 
  mutate(value20 = ifelse(`y2020-21` != 0, residuals, 0),
         value21 = ifelse(`y2021-22` != 0, residuals, 0),
         value22 = ifelse(`y2022-23` != 0, residuals, 0),
         value23 = ifelse(`y2023-24` != 0, residuals, 0),
         value24 = ifelse(`y2024-25` != 0, residuals, 0)) %>%
  mutate(cumValue = value20 + value21 + value22 + value23 + value24) %>% 
  select(player, cumValue, gsd2_fppg_bbr, `y2021-22`, `y2022-23`, `y2023-24`, `y2024-25`, age, everything()) %>% 
  arrange(-cumValue)
tmp_data

# THIS IS CURRENTLY WRONG BC THE RESIDUALS ON ROOKIE DEALS WON'T APPLY TO EXTENSIONS, ETC. 
```

Check for missingness 

```{r}
gsd2_data %>% summarise_all(~ sum(is.na(.)))
```

Check the distribution of the outcome variable 

```{r, fig.width=10, fig.height=4}
plot_skewed <- ggplot(gsd2_data, aes(x = gsd2_fppg_bbr)) +
    geom_histogram(bins = 50) +
    labs(x = "Fantasy Points Per Game",
         y = "Number of Players") +
  theme_minimal() + 
  ggtitle("Original Distribution is Skewed")

plot_sqrt <- ggplot(gsd2_data, aes(x = gsd2_fppg_bbr)) +
    geom_histogram(bins = 50) +
    labs(x = "Fantasy Points Per Game",
         y = "Number of Players") +
  theme_minimal() +
  scale_x_sqrt() + 
  ggtitle("Distribution after Square-Root Transformation")

plot_grid(plot_skewed, plot_sqrt, labels = c('A', 'B'), label_size = 12)
```

```{r}
gsd2_data <- gsd2_data %>% 
  mutate_if(is.character, as.factor) %>% 
  mutate(pos_pg = ifelse(str_detect(position, "\\b(?i)(PG)\\b"), "1", "0"),
         pos_sg = ifelse(str_detect(position, "\\b(?i)(SG)\\b"), "1", "0"),
         pos_sf = ifelse(str_detect(position, "\\b(?i)(SF)\\b"), "1", "0"),
         pos_pf = ifelse(str_detect(position, "\\b(?i)(PF)\\b"), "1", "0"),
         pos_c = ifelse(str_detect(position, "\\b(?i)(C)\\b"), "1", "0"),
         pos_pg = as.numeric(pos_pg),
         pos_sg = as.numeric(pos_sg),
         pos_sf = as.numeric(pos_sf),
         pos_pf = as.numeric(pos_pf),
         pos_c = as.numeric(pos_c)) %>% 
  select(year, age, games, team, per, ts_percent, orb_percent, drb_percent, ast_percent, vorp,
         stl_percent, blk_percent, tov_percent, usg_percent, fg_percent, ft_percent, x3p_percent, 
         pos_pg, pos_sg, pos_sf, pos_sf, pos_pf, pos_c, gsd2_fppg_bbr) %>% 
  filter(gsd2_fppg_bbr > 0) %>% 
  mutate(team = as.factor(team), 
         gsd2_fppg_bbr = sqrt(gsd2_fppg_bbr)
         )
```

```{r}
set.seed(1234)
gsd2_split <- gsd2_data %>%
    initial_split(prop = 0.8)

gsd2_train <- training(gsd2_split)
gsd2_test <- testing(gsd2_split)
```

```{r}
## a linear regression model specification
lm_spec <- linear_reg() %>%
    set_engine("lm")

lm_fit <- lm_spec %>%
    fit(gsd2_fppg_bbr ~ ., data = gsd2_train)

tidy(lm_fit) %>% arrange(-estimate)
```
```{r}
broom::glance(lm_fit)
```


```{r}
## a random forest model specification
rf_spec <- rand_forest() %>%
    set_mode("regression") %>%
    set_engine("randomForest")

fit_rf <- rf_spec %>%
    fit(gsd2_fppg_bbr ~ ., data = gsd2_train)

fit_rf
```

```{r}
results_train <- lm_fit %>%
  predict(new_data = gsd2_train) %>%
  mutate(truth = gsd2_train$gsd2_fppg_bbr,
         model = "lm") %>%
  bind_rows(fit_rf %>%
              predict(new_data = gsd2_train) %>%
              mutate(truth = gsd2_train$gsd2_fppg_bbr, 
                     model = "rf"))
results_train %>% 
  mutate(.pred = .pred^2, truth = truth^2)
```
```{r}
results_test <- lm_fit %>%
  predict(new_data = gsd2_test) %>%
  mutate(truth = gsd2_test$gsd2_fppg_bbr,
         model = "lm") %>%
  bind_rows(fit_rf %>%
    predict(new_data = gsd2_test) %>%
    mutate(truth = gsd2_test$gsd2_fppg_bbr,
           model = "rf"))
results_test %>% 
  mutate(.pred = .pred^2, truth = truth^2)
```

```{r}
results_train %>%
  group_by(model) %>%
  rmse(truth = truth, estimate = .pred)
```
```{r}
results_test %>%
  group_by(model) %>%
  rmse(truth = truth, estimate = .pred)
```

this shows that our linear model did about the same on the test data 
but the random forest model did not perform the same 

```{r, fig.width=10, fig.height=4}
results_test %>%
  mutate(train = "testing") %>%
  bind_rows(results_train %>%
    mutate(train = "training")) %>%
  ggplot(aes(truth, .pred, color = model)) +
  geom_abline(lty = 2, color = "gray80", size = 1.5) +
  geom_point(alpha = 0.5) +
  facet_wrap(~train) +
  labs(
    x = "Truth",
    y = "Predicted attendance",
    color = "Type of model"
  ) + theme_minimal()
```

Because the random forest did not perform well, we can resample on the training set. We will use crossfold evalations, which partitions the data into 10 folds. We can then train the data on 9 folds and compare against the tenth.

```{r}
nba_folds <- vfold_cv(gsd2_train, strata = team)

rf_results <- fit_resamples(
  gsd2_fppg_bbr ~ ., 
  rf_spec, 
  nba_folds, 
  control = control_resamples(save_pred = TRUE))

# lets compare the mean rmse in these new results... 
rf_results %>% 
  collect_metrics()
```
```{r}
# with our older results from the testing data
results_test %>%
  group_by(model) %>%
  rmse(truth = truth, estimate = .pred)
```
```{r, fig.height=4}
rf_results %>% 
  unnest(.predictions) %>% 
  ggplot(aes(gsd2_fppg_bbr, .pred)) +
    geom_abline(lty = 2, color = "gray50") +
    geom_point(aes(color = id), size = 1.5, alpha = 0.3, show.legend = FALSE) +
    geom_smooth(method = "lm") + theme_minimal()
```

```{r}
new_results <- results_test %>% 
  mutate(.pred = .pred^2, truth = truth^2) %>% 
  bind_rows(rf_results %>% 
              unnest(.predictions) %>% 
              mutate(.pred = .pred^2, 
                     truth = gsd2_fppg_bbr^2,
                     model = "rf_rs") %>% 
              select(.pred, truth, model))
new_results

new_results %>%
  group_by(model) %>%
  rmse(truth = truth, estimate = .pred)
```








```{r, fig.width=10, fig.height=5}
prediction_data <- gsd2_data %>% filter(games > 5 & gsd2_fppg_bbr > 18)
fit <- lm(gsd2_fppg_bbr ~ salary, data=prediction_data) # fit the model
prediction_data$predicted <- predict(fit)   # Save the predicted values
prediction_data$residuals <- residuals(fit) # Save the residual values

prediction_data <- arrange(prediction_data, desc(residuals)) %>%
  mutate(rank = 1:nrow(prediction_data)) %>% 
  select(rank, player, position, age, gsd2_fppg_bbr, residuals, games, everything()) %>% 
  mutate(player_label = ifelse(residuals > 10 & year > 2018, player, NA))

ggplot(prediction_data, aes(x = salary, y = gsd2_fppg_bbr)) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +      
  geom_segment(aes(xend = salary, yend = predicted), alpha = .2) +   
  geom_point(aes(color = abs(residuals), size = abs(residuals))) + 
  geom_text(aes(label=player_label), size=3, hjust=0.5, vjust=0) +
  scale_color_continuous(low = "#386890", high = "#40E0D0") +     
  guides(color = FALSE, size = FALSE) +                             
  geom_point(aes(y = predicted), shape = 1) +
  scale_x_continuous(breaks = c(0, 5000000, 10000000, 15000000, 20000000, 25000000, 30000000, 35000000),
                     labels = c("0M", "5M", "10M", "15M", "20M", "25M", "30M", "35M")) +
  theme_minimal()
```
```{r}
prediction_data %>% 
  select(rank, player, position, age, gsd2_fppg_bbr, residuals, salary, year, everything()) %>% 
  filter(age < 22 & games > 5 & gsd2_fppg_bbr > 18)
```
```{r}
salaries <- forthcoming_salaries %>% 
  rename(player = Player) %>% 
  clean_nba_names() 

tmp_data <- prediction_data %>% 
  filter(year == 2019) %>% 
  select(player, gsd2_fppg_bbr, age, residuals, predicted, team)

tmp_data %>% 
  left_join(salaries, by = "player") %>% 
  select(-`Signed Using`, -Rk, -playerID, -Tm, -Guaranteed) %>% 
  mutate(`y2021-22` = replace_na(`y2021-22`, 0),
         `y2022-23` = replace_na(`y2022-23`, 0)) %>% 
  mutate(test20 = ifelse(`y2020-21` != 0, residuals, 0),
         test21 = ifelse(`y2021-22` != 0, residuals, 0),
         test22 = ifelse(`y2022-23` != 0, residuals, 0),
         test23 = ifelse(`y2023-24` != 0, residuals, 0)) %>%
  mutate(test_all = test20 + test21 + test22 + test23) %>% 
  select(player, test_all, everything()) %>% 
  arrange(-test_all)


```








```{r}
two_years <- prediction_data %>% filter(games > 5 & gsd2_fppg_bbr > 18)
mean(two_years$residuals)
position_count <- two_years %>% 
  mutate(position = str_replace_all(position, "PF-C", "PF"),
         position = str_replace_all(position, "SF-PF", "SF"),
         position = str_replace_all(position, "SF-SG", "SF"),
         position = str_replace_all(position, "PF-SF", "SF")) %>% 
  group_by(position) %>%
  count() %>% 
  rename(player_count = n) %>% 
  arrange(-player_count); position_count

two_years %>% 
  mutate(position = str_replace_all(position, "PF-C", "PF"),
         position = str_replace_all(position, "SF-PF", "SF"),
         position = str_replace_all(position, "SF-SG", "SF"),
         position = str_replace_all(position, "PF-SF", "SF")) %>%  
  group_by(position) %>%
  summarize(fppg_by_position = sum(gsd2_fppg_bbr)) %>% 
  left_join(position_count, by = "position") %>% 
  mutate(ffpg_normed = fppg_by_position / player_count) %>% 
  arrange(fppg_by_position)
```

*next steps* 
contract data for coming years 
projections for current nba players based on similar players???






















