---
title: "Legacy Dynasty Fantasy Tools"
author: "Brandon L. Kramer"
date: "8/29/2019"
output: html_document
---

This file contains the following materials for Legacy Dynasty NBA fantasy points league 

* Concatenation of Basketball Reference (2018), Hashtag (2019), and Hashtag Alt (2019) Projections
* Overall Stats and Projections
* Contract Value Calculator
* Team Projections
* Team Players Quick Comparisons 
* Post-Trade Comparison Tool 

```{r pull packages and projection data, warning=FALSE, eval=FALSE}
#install.packages("tidyverse"); install.packages("googlesheets")
rm(list = ls())
for (pkg in c("googlesheets", "tidyverse")) {library(pkg, character.only = TRUE)}
(my_sheets <- gs_ls())

bballref18 <- gs_url("https://docs.google.com/spreadsheets/d/13EnBmUWDmxJ86xFzCpaHUuXGW0KADW_bDUVLf0dWFgA/edit#gid=58340951") %>% 
  gs_read(ws = "bballref18") 

bballref18$player <- bballref18$player %>% 
  str_replace_all(c('Á' = 'A', 'ā' = 'a', 'á' = 'a', 'č' = 'c', 'ć' = 'c', 'è' = 'e', 
                    'é' = 'e', 'ê' = 'e', 'ić' = 'ic', 'ö' = 'o', 'ó' = 'o', 'Š' = 'S', 
                    'š' = 's', 'ū' = 'u', 'ý' = 'y', 'Ž' = 'Z', 'ž' = 'z', 
                    'Élie' = 'Elie','P.J.' = 'PJ','C.J.' = 'CJ', 'R.J.' = 'RJ', 'T.J.' = 'TJ', 
                    'D.J.' = 'DJ', 'J.J.' = 'JJ', 'Dončić' = 'Doncic', 'Louis' = 'Lou', 'Edrice' = 'Bam', 
                    'Waller-Prince' = 'Prince', "O.G." = "OG", "Demarre" = "DeMarre",
                    'Jaren Jackson' = 'Jaren Jackson Jr.','Kelly Oubre' = 'Kelly Oubre Jr.', 
                    'Marvin Bagley' = 'Marvin Bagley III', 'Otto Porter' = 'Otto Porter Jr.', 
                    'Wendell Carter' = 'Wendell Carter Jr.', 'Larry Nance' = 'Larry Nance Jr.',
                    'Walt Lemon' = 'Walt Lemon Jr.', 'Dennis Schröder' = 'Dennis Schroder', 
                    'Tim Hardaway' = 'Tim Hardaway Jr.'))

combined_data <- bballref18 %>% 
  rename(bbr_pts = "PTS", bbr_dreb = "DRB", bbr_orb = "ORB",
         bbr_ast = "AST", bbr_stl = "STL", bbr_blk = "BLK",
         bbr_tov = "TOV", bbr_threes = "3P", bbr_fga = "FGA",
         bbr_fgm = "FG", bbr_ftm = "FT",  bbr_fta = "FTA", bbr_gms = "G", bbr_mpg = "MP", age = "Age") %>%
  mutate(bbr_ld_fpts = bbr_pts + (bbr_dreb*1.5) + (bbr_orb*2) + (bbr_ast*2) + (bbr_stl*2.5) + (bbr_blk*2.5) +
         (bbr_tov*-1) + bbr_threes + (bbr_fga*-0.5) + (bbr_fgm*0.5) + bbr_ftm + (bbr_fta*-1)) %>%
  mutate(bbr_fr_fpts = bbr_pts + (bbr_dreb*1.5) + (bbr_orb*2) + (bbr_ast*2) + (bbr_stl*2.5) + (bbr_blk*2.5) +
         (bbr_tov*-1) + bbr_threes + (bbr_fga*-0.5) + (bbr_fgm*0.5) + bbr_ftm + (bbr_fta*-1)) %>% 
  mutate(bbr_gsd2_fpts = bbr_pts + bbr_dreb + (bbr_orb*1.25) + (bbr_ast*1.5) + (bbr_stl*1.5) + (bbr_blk*2) +
         (bbr_tov*-1)+bbr_threes+(bbr_fga*-0.5)+(bbr_fgm*0.5)+(bbr_ftm*0.5)+(bbr_fta*-0.75)) %>%
  mutate(bbr_botb_fpts = bbr_pts + bbr_dreb + (bbr_orb*1.25) + (bbr_ast*1.5) + (bbr_stl*1.5) + (bbr_blk*2) +
         (bbr_tov*-1)+bbr_threes+(bbr_fga*-0.5)+(bbr_fgm*0.5)+(bbr_ftm*0.5)+(bbr_fta*-0.75)) %>% 
  select(player, age, bbr_ld_fpts, bbr_fr_fpts, bbr_gsd2_fpts, bbr_botb_fpts, bbr_gms, bbr_mpg,
         bbr_pts, bbr_dreb, bbr_orb, bbr_ast, bbr_stl, bbr_blk, bbr_tov, bbr_threes, bbr_fga, bbr_fgm, bbr_ftm, bbr_fta)

hashalt19 <- gs_url("https://docs.google.com/spreadsheets/d/13EnBmUWDmxJ86xFzCpaHUuXGW0KADW_bDUVLf0dWFgA/edit#gid=2083425618") %>% gs_read(ws = "2019_hashtag_alt_proj") 

hashalt19$player <- hashalt19$player %>% 
  str_replace_all(c('Á' = 'A', 'ā' = 'a', 'á' = 'a', 'č' = 'c', 'ć' = 'c', 'è' = 'e', 'é' = 'e', 'ê' = 'e',
                    'ö' = 'o', 'ó' = 'o', 'Š' = 'S', 'š' = 's', 'ū' = 'u', 'ý' = 'y', 'Ž' = 'Z', 'ž' = 'z',
                    'P.J.' = 'PJ','C.J.' = 'CJ', 'R.J.' = 'RJ', 'T.J.' = 'TJ', 'D.J.' = 'DJ', 'J.J.' = 'JJ',
                    'Louis' = 'Lou', 'Edrice' = 'Bam', 'Waller-Prince' = 'Prince', "O.G." = "OG", 
                    'Jaren Jackson' = 'Jaren Jackson Jr.','Kelly Oubre' = 'Kelly Oubre Jr.', 
                    'Marvin Bagley' = 'Marvin Bagley III', 'Otto Porter' = 'Otto Porter Jr.', 
                    'Wendell Carter' = 'Wendell Carter Jr.', 'Larry Nance' = 'Larry Nance Jr.',
                    'Walt Lemon' = 'Walt Lemon Jr.', 'Dennis Schröder' = 'Dennis Schroder', 
                    'Tim Hardaway' = 'Tim Hardaway Jr.', "Demarre" = "DeMarre"))

hashalt19 <- hashalt19 %>% 
  rename(hta_pts = "PTS", hta_treb = "REB", hta_ast = "AST", hta_stl = "STL", hta_blk = "BLK",
         hta_tov = "TOV", hta_threes = "THREES", hta_fga = "FGA",hta_fgm = "FGM", hta_ftm = "FTM",  
         hta_fta = "FTA", hta_mpg = "MPG", hta_ftp = "FT", hta_gms = "Gs") %>%
  mutate(hta_dreb = hta_treb*0.78) %>% 
  mutate(hta_orb = hta_treb*0.22) %>% 
  mutate(hta_ld_fpts = hta_pts + (hta_dreb*1.5) + (hta_orb*2) + (hta_ast*2) + (hta_stl*2.5) + (hta_blk*2.5) +
         (hta_tov*-1) + hta_threes + (hta_fga*-0.5) + (hta_fgm*0.5) + hta_ftm + (hta_fta*-1)) %>%
  mutate(hta_fr_fpts = hta_pts + (hta_dreb*1.5) + (hta_orb*2) + (hta_ast*2) + (hta_stl*2.5) + (hta_blk*2.5) +
         (hta_tov*-1) + hta_threes + (hta_fga*-0.5) + (hta_fgm*0.5) + hta_ftm + (hta_fta*-1)) %>% 
  mutate(hta_gsd2_fpts = hta_pts + hta_dreb + (hta_orb*1.25) + (hta_ast*1.5) + (hta_stl*1.5) + (hta_blk*2) +
         (hta_tov*-1)+hta_threes+(hta_fga*-0.5)+(hta_fgm*0.5)+(hta_ftm*0.5)+(hta_fta*-0.75)) %>%
  mutate(hta_botb_fpts = hta_pts + hta_dreb + (hta_orb*1.25) + (hta_ast*1.5) + (hta_stl*1.5) + (hta_blk*2) +
         (hta_tov*-1)+hta_threes+(hta_fga*-0.5)+(hta_fgm*0.5)+(hta_ftm*0.5)+(hta_fta*-0.75)) %>% 
  select(player, hta_ld_fpts, hta_fr_fpts, hta_gsd2_fpts, hta_botb_fpts, hta_gms, hta_mpg, 
         hta_pts, hta_dreb, hta_orb, hta_ast, hta_stl, hta_blk, hta_tov, hta_threes, hta_fga, hta_fgm, hta_ftm, hta_fta, hta_ftp)
  
combined_data <- combined_data %>% 
  full_join(hashalt19, by = "player")

hashtag19 <- gs_url("https://docs.google.com/spreadsheets/d/13EnBmUWDmxJ86xFzCpaHUuXGW0KADW_bDUVLf0dWFgA/edit#gid=665288709") %>% gs_read(ws = "2019_hashtag_proj") 

hashtag19$player <- hashtag19$player %>% 
  str_replace_all(c('Á' = 'A', 'ā' = 'a', 'á' = 'a', 'č' = 'c', 'ć' = 'c', 'è' = 'e', 'é' = 'e', 'ê' = 'e',
                    'ö' = 'o', 'ó' = 'o', 'Š' = 'S', 'š' = 's', 'ū' = 'u', 'ý' = 'y', 'Ž' = 'Z', 'ž' = 'z',
                    'P.J.' = 'PJ','C.J.' = 'CJ', 'R.J.' = 'RJ', 'T.J.' = 'TJ', 'D.J.' = 'DJ', 'J.J.' = 'JJ',
                    'Louis' = 'Lou', 'Edrice' = 'Bam', 'Waller-Prince' = 'Prince', "O.G." = "OG", 
                    "Demarre" = "DeMarre",'Dennis Schröder' = 'Dennis Schroder'))

hashtag19 <- hashtag19 %>% 
  rename(ht_pts = "PTS", ht_dreb = "DREB", ht_orb = "OREB", ht_ast = "AST", ht_stl = "STL", ht_blk = "BLK",
         ht_tov = "TO", ht_threes = "THREES", ht_fga = "FGA", ht_fgm = "FGM", ht_ftm = "FTM",  
         ht_fta = "FTA", ht_mpg = "MPG", ht_gms = "GP", ht_fgp = "FG%", ht_ftp = "FT%", team = "TEAM") %>%
  mutate(ht_ld_fpts = ht_pts + (ht_dreb*1.5) + (ht_orb*2) + (ht_ast*2) + (ht_stl*2.5) + (ht_blk*2.5) +
         (ht_tov*-1) + ht_threes + (ht_fga*-0.5) + (ht_fgm*0.5) + ht_ftm + (ht_fta*-1)) %>%
  mutate(ht_fr_fpts = ht_pts + (ht_dreb*1.5) + (ht_orb*2) + (ht_ast*2) + (ht_stl*2.5) + (ht_blk*2.5) +
         (ht_tov*-1) + ht_threes + (ht_fga*-0.5) + (ht_fgm*0.5) + ht_ftm + (ht_fta*-1)) %>% 
  mutate(ht_gsd2_fpts = ht_pts + ht_dreb + (ht_orb*1.25) + (ht_ast*1.5) + (ht_stl*1.5) + (ht_blk*2) +
         (ht_tov*-1)+ht_threes+(ht_fga*-0.5)+(ht_fgm*0.5)+(ht_ftm*0.5)+(ht_fta*-0.75)) %>%
  mutate(ht_botb_fpts = ht_pts + ht_dreb + (ht_orb*1.25) + (ht_ast*1.5) + (ht_stl*1.5) + (ht_blk*2) +
         (ht_tov*-1)+ht_threes+(ht_fga*-0.5)+(ht_fgm*0.5)+(ht_ftm*0.5)+(ht_fta*-0.75)) %>% 
  select(player, team, ht_ld_fpts, ht_fr_fpts, ht_gsd2_fpts, ht_botb_fpts, ht_gms, ht_mpg, 
         ht_pts, ht_dreb, ht_orb, ht_ast, ht_stl, ht_blk, ht_tov, ht_threes, ht_fga, ht_fgm, ht_fgp, ht_ftm, ht_fta, ht_ftp)

combined_data <- combined_data %>% 
  full_join(hashtag19, by = "player")

legacy_contracts <- gs_url("https://docs.google.com/spreadsheets/d/13EnBmUWDmxJ86xFzCpaHUuXGW0KADW_bDUVLf0dWFgA/edit#gid=0") %>% gs_read(ws = "legacy_contracts") 

legacy_contracts$player <- legacy_contracts$player %>% 
  str_replace_all(c('C.J.' = 'CJ', 'R.J.' = 'RJ', 'T.J.' = 'TJ', 'D.J.' = 'DJ', "O.G." = "OG", "Demarre" = "DeMarre",
                    'Louis' = 'Lou', 'Edrice' = 'Bam', 'Waller-Prince' = 'Prince', 
                    'Á' = 'A', 'ā' = 'a', 'á' = 'a', 'č' = 'c', 'ć' = 'c', 'è' = 'e', 'é' = 'e', 'ê' = 'e',
                    'ö' = 'o', 'ó' = 'o', 'Š' = 'S', 'š' = 's', 'ū' = 'u', 'ý' = 'y', 'Ž' = 'Z', 'ž' = 'z',
                    'P.J.' = 'PJ','C.J.' = 'CJ', 'R.J.' = 'RJ', 'T.J' = 'TJ', 'D.J.' = 'DJ', 'J.J.' = 'JJ'))

combined_data <- combined_data %>% 
  full_join(legacy_contracts, by = "player")

select_data <- combined_data %>% 
  select(player, age, team,
         bbr_ld_fpts, bbr_gms, bbr_mpg, hta_ld_fpts, hta_gms, hta_mpg, ht_ld_fpts, ht_gms, ht_mpg, 
         ld_team, ld_2019, ld_2020, ld_2021, ld_2022, ld_2023, ld_2024, ld_rfa, ld_gleague, ld_intl, trade_comp)
rm(bballref18, hashtag19, hashalt19, legacy_contracts, my_sheets)

nba_schedule <- gs_url("https://docs.google.com/spreadsheets/d/13EnBmUWDmxJ86xFzCpaHUuXGW0KADW_bDUVLf0dWFgA/edit#gid=1604050216") %>% 
  gs_read(ws = "2019_nba_schedule")

```

# LD Overall Stats and Projections  

```{r looking at overall projections}
select_data %>% 
  #filter(bbr_gms > 50) %>%
  #filter(bbr_ld_fpts > 25) %>%
  #filter(hta_ld_fpts > 25) %>%
  #filter(ht_ld_fpts > 25) %>%
  #filter(age < 25) %>% 
  #arrange(-bbr_ld_fpts) %>% 
  #arrange(-hta_ld_fpts) %>% 
  arrange(-ht_ld_fpts) %>% 
  select(player, age, bbr_ld_fpts, hta_ld_fpts, ht_ld_fpts, ld_2019, ld_2020, ld_2021, ld_rfa, ld_gleague, ld_intl)
```

## LD Contract Value Calculators

```{r bballref evaluations in ld}
select_data %>% 
  mutate(bbr_ld_value_19 = bbr_ld_fpts / ld_2019) %>% 
  mutate(bbr_ld_value_20 = bbr_ld_fpts / ld_2020) %>%
  mutate(bbr_ld_value_21 = bbr_ld_fpts / ld_2021) %>%
  #filter(bbr_gms > 50) %>%
  #filter(bbr_ld_fpts > 25) %>% 
  #filter(age < 25) %>% 
  arrange(-bbr_ld_value_19) %>% 
  select(player, age, bbr_ld_fpts, bbr_ld_value_19, bbr_ld_value_20, bbr_ld_value_21, 
         ld_2019, ld_2020, ld_2021, ld_rfa, ld_gleague, ld_intl)
```

```{r hashtag_alt evaluations in ld}
select_data %>% 
  mutate(hta_ld_value_19 = hta_ld_fpts / ld_2019) %>% 
  mutate(hta_ld_value_20 = hta_ld_fpts / ld_2020) %>%
  mutate(hta_ld_value_21 = hta_ld_fpts / ld_2021) %>%
  filter(hta_ld_fpts > 25) %>% 
  #filter(age < 25) %>% 
  arrange(-hta_ld_value_19) %>% 
  select(player, age, hta_ld_fpts, hta_ld_value_19, hta_ld_value_20, hta_ld_value_21, 
         ld_2019, ld_2020, ld_2021, ld_rfa, ld_gleague, ld_intl)
```

```{r hashtag evaluations in ld}
select_data %>% 
  mutate(ht_ld_value_19 = ht_ld_fpts / ld_2019) %>% 
  mutate(ht_ld_value_20 = ht_ld_fpts / ld_2020) %>%
  mutate(ht_ld_value_21 = ht_ld_fpts / ld_2021) %>%
  filter(ht_ld_fpts > 25) %>% 
  #filter(age < 25) %>% 
  arrange(-ht_ld_value_19) %>% 
  select(player, age, ht_ld_fpts, ht_ld_value_19, ht_ld_value_20, ht_ld_value_21, 
         ld_2019, ld_2020, ld_2021, ld_rfa, ld_gleague, ld_intl)
```

## LD Team Projections 

LD Team Projections BBR

```{r ld 2018 bbr projections, fig.width=11, fig.height=6, warning=FALSE}
ld_temp_1 <- select_data %>% 
  filter(ld_gleague == "0") %>% 
  filter(ld_intl == "0") %>% 
  group_by(ld_team) %>% summarize(avg_fppg = mean(bbr_ld_fpts, na.rm = TRUE))  
ld_temp_2 <- select_data %>% 
  filter(ld_gleague == "0") %>% 
  filter(ld_intl == "0") %>% 
  group_by(ld_team) %>% summarize(ld_players = n()) %>% filter(ld_team != "NA")
ld_bbr_team_projections <- full_join(ld_temp_1, ld_temp_2, by = "ld_team") %>% 
  mutate(team_total = avg_fppg * ld_players) %>% 
  arrange(-team_total); rm(ld_temp_1, ld_temp_2)
ld_bbr_team_projections
ggplot(data=ld_bbr_team_projections, aes(x=reorder(ld_team, -team_total), y=team_total, fill=ld_team)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  theme_bw() +
  theme(axis.title.x=element_blank(), axis.title.y=element_blank()) +
  geom_text(aes(label = ld_players), size = 3, colour="white", fontface="bold", hjust = 0.5, vjust = 3) +
  labs(title = "Legacy Dynasty Rankings - Projected Team Points Per Week (Based on 2018 Stats)", 
       fill = "LD Team Name") +
  scale_fill_manual(values=c("#C8102E", "#061922", "#008348", "#00788C", "#ce1141", 
                             "#860038", "#007dc5", "#0E2240", "#C8102E", "#1D428A",
                             "#ce1141", "#ffc633", "#1D428A", "#552582", "#5D76A9", 
                             "#98002e", "#00471b", "#78be20", "#b6995a", "#F58426",
                             "#EF3B24", "#007dc5", "#006bb6", "#e56020", "#000000", 
                             "#724c9f", "#bac3c9", "#ce1141", "#002B5C", "#002b5c")) 
ggplot(data=ld_bbr_team_projections, aes(x=reorder(ld_team, -avg_fppg), y=avg_fppg, fill=ld_team)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  theme_bw() +
  theme(axis.title.x=element_blank(), axis.title.y=element_blank()) +
  geom_text(aes(label = ld_players), size = 3, colour="white", fontface="bold", hjust = 0.5, vjust = 3) +
  labs(title = "Legacy Dynasty Rankings - Avg Fantasy Points Per Player (Based on 2018 Stats)", 
       fill = "LD Team Name") +
  scale_fill_manual(values=c("#C8102E", "#061922", "#008348", "#00788C", "#ce1141", 
                             "#860038", "#007dc5", "#0E2240", "#C8102E", "#1D428A",
                             "#ce1141", "#ffc633", "#1D428A", "#552582", "#5D76A9", 
                             "#98002e", "#00471b", "#78be20", "#b6995a", "#F58426",
                             "#EF3B24", "#007dc5", "#006bb6", "#e56020", "#000000", 
                             "#724c9f", "#bac3c9", "#ce1141", "#002B5C", "#002b5c"))
```

LD Team Projections HashTag Alt 

```{r ld 2019 hta projections, fig.width=11, fig.height=6, warning=FALSE}
ld_temp_1 <- select_data %>% 
  filter(ld_gleague == "0") %>% 
  filter(ld_intl == "0") %>% 
  group_by(ld_team) %>% summarize(avg_fppg = mean(hta_ld_fpts, na.rm = TRUE))  
ld_temp_2 <- select_data %>% 
  filter(ld_gleague == "0") %>% 
  filter(ld_intl == "0") %>% 
  group_by(ld_team) %>% summarize(ld_players = n()) %>% filter(ld_team != "NA")
ld_hta_team_projections <- full_join(ld_temp_1, ld_temp_2, by = "ld_team") %>% 
  mutate(team_total = avg_fppg * ld_players) %>% 
  arrange(-team_total); rm(ld_temp_1, ld_temp_2)
ld_hta_team_projections
ggplot(data=ld_hta_team_projections, aes(x=reorder(ld_team, -team_total), y=team_total, fill=ld_team)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  theme_bw() +
  theme(axis.title.x=element_blank(), axis.title.y=element_blank()) +
  geom_text(aes(label = ld_players), size = 3, colour="white", fontface="bold", hjust = 0.5, vjust = 3) +
  labs(title = "Legacy Dynasty Rankings - Projected Team Points Per Week (Based on 2019 HTA Stats)", 
       fill = "LD Team Name") +
  scale_fill_manual(values=c("#C8102E", "#061922", "#008348", "#00788C", "#ce1141", 
                             "#860038", "#007dc5", "#0E2240", "#C8102E", "#1D428A",
                             "#ce1141", "#ffc633", "#1D428A", "#552582", "#5D76A9", 
                             "#98002e", "#00471b", "#78be20", "#b6995a", "#F58426",
                             "#EF3B24", "#007dc5", "#006bb6", "#e56020", "#000000", 
                             "#724c9f", "#bac3c9", "#ce1141", "#002B5C", "#002b5c")) 
ggplot(data=ld_hta_team_projections, aes(x=reorder(ld_team, -avg_fppg), y=avg_fppg, fill=ld_team)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  theme_bw() +
  theme(axis.title.x=element_blank(), axis.title.y=element_blank()) +
  geom_text(aes(label = ld_players), size = 3, colour="white", fontface="bold", hjust = 0.5, vjust = 3) +
  labs(title = "Legacy Dynasty Rankings - Avg Fantasy Points Per Player (Based on 2019 HTA Stats)", fill = "LD Team Name") +
  scale_fill_manual(values=c("#C8102E", "#061922", "#008348", "#00788C", "#ce1141", 
                             "#860038", "#007dc5", "#0E2240", "#C8102E", "#1D428A",
                             "#ce1141", "#ffc633", "#1D428A", "#552582", "#5D76A9", 
                             "#98002e", "#00471b", "#78be20", "#b6995a", "#F58426",
                             "#EF3B24", "#007dc5", "#006bb6", "#e56020", "#000000", 
                             "#724c9f", "#bac3c9", "#ce1141", "#002B5C", "#002b5c"))
```

LD Team Projections HashTag 

```{r ld 2019 ht projections, fig.width=11, fig.height=6, warning=FALSE}
ld_temp_1 <- select_data %>% 
  filter(ld_gleague == "0") %>% 
  filter(ld_intl == "0") %>%  
  group_by(ld_team) %>% summarize(avg_fppg = mean(ht_ld_fpts, na.rm = TRUE))  
ld_temp_2 <- select_data %>% 
  filter(ld_gleague == "0") %>% 
  filter(ld_intl == "0") %>% 
  group_by(ld_team) %>% summarize(ld_players = n()) %>% filter(ld_team != "NA")
ld_ht_team_projections <- full_join(ld_temp_1, ld_temp_2, by = "ld_team") %>% 
  mutate(team_total = avg_fppg * ld_players) %>% 
  arrange(-team_total); rm(ld_temp_1, ld_temp_2)
ld_ht_team_projections
ggplot(data=ld_ht_team_projections, aes(x=reorder(ld_team, -team_total), y=team_total, fill=ld_team)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  theme_bw() +
  theme(axis.title.x=element_blank(), axis.title.y=element_blank()) +
  geom_text(aes(label = ld_players), size = 3, colour="white", fontface="bold", hjust = 0.5, vjust = 3) +
  labs(title = "Legacy Dynasty Rankings - Projected Team Points Per Week (Based on 2019 HT Stats)", 
       fill = "LD Team Name") +
  scale_fill_manual(values=c("#C8102E", "#061922", "#008348", "#00788C", "#ce1141", 
                             "#860038", "#007dc5", "#0E2240", "#C8102E", "#1D428A",
                             "#ce1141", "#ffc633", "#1D428A", "#552582", "#5D76A9", 
                             "#98002e", "#00471b", "#78be20", "#b6995a", "#F58426",
                             "#EF3B24", "#007dc5", "#006bb6", "#e56020", "#000000", 
                             "#724c9f", "#bac3c9", "#ce1141", "#002B5C", "#002b5c")) 
ggplot(data=ld_ht_team_projections, aes(x=reorder(ld_team, -avg_fppg), y=avg_fppg, fill=ld_team)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  theme_bw() +
  theme(axis.title.x=element_blank(), axis.title.y=element_blank()) +
  geom_text(aes(label = ld_players), size = 3, colour="white", fontface="bold", hjust = 0.5, vjust = 3) +
  labs(title = "Legacy Dynasty Rankings - Avg Fantasy Points Per Player (Based on 2019 HT Stats)", 
       fill = "LD Team Name") +
  scale_fill_manual(values=c("#C8102E", "#061922", "#008348", "#00788C", "#ce1141", 
                             "#860038", "#007dc5", "#0E2240", "#C8102E", "#1D428A",
                             "#ce1141", "#ffc633", "#1D428A", "#552582", "#5D76A9", 
                             "#98002e", "#00471b", "#78be20", "#b6995a", "#F58426",
                             "#EF3B24", "#007dc5", "#006bb6", "#e56020", "#000000", 
                             "#724c9f", "#bac3c9", "#ce1141", "#002B5C", "#002b5c"))
```

## Team Players Quick Comparisons

```{r looking at specific team's players projections}
select_data %>% 
  mutate(ht_ld_value_19 = ht_ld_fpts / ld_2019) %>% 
  mutate(ht_ld_value_20 = ht_ld_fpts / ld_2020) %>%
  mutate(ht_ld_value_21 = ht_ld_fpts / ld_2021) %>%
  filter(ld_team == "DAL") %>% 
  arrange(-ht_ld_value_19) %>% 
  select(player, age, ld_team, bbr_ld_fpts, hta_ld_fpts, ht_ld_fpts, ht_ld_value_19, 
         ld_2019, ld_2020, ld_2021, ld_2022, ld_2023, ld_2024, ld_rfa, ld_gleague, ld_intl)
```

```{r looking at specific team's players projections}
select_data %>% 
  mutate(ht_ld_value_19 = ht_ld_fpts / ld_2019) %>% 
  mutate(ht_ld_value_20 = ht_ld_fpts / ld_2020) %>%
  mutate(ht_ld_value_21 = ht_ld_fpts / ld_2021) %>%
  filter(ld_team == "MIN") %>% 
  arrange(-ht_ld_value_19) %>% 
  select(player, age, ld_team, bbr_ld_fpts, hta_ld_fpts, ht_ld_fpts, ht_ld_value_19, 
         ld_2019, ld_2020, ld_2021, ld_2022, ld_2023, ld_2024, ld_rfa, ld_gleague, ld_intl, )
```

## Post-Trade Comparison Tool

Post-Trade Comparison Tool HashTag Alt 

```{r comparing team projections before and after trade using hta, fig.width=11, fig.height=6, warning=FALSE}
temp_1 <- select_data %>% 
  filter(ld_gleague == "0") %>% 
  filter(ld_intl == "0") %>%  
  group_by(ld_team) %>% summarize(avg_fppg = mean(hta_ld_fpts, na.rm = TRUE)) 
temp_2 <- select_data %>% 
  filter(ld_gleague == "0") %>% 
  filter(ld_intl == "0") %>% 
  group_by(ld_team) %>% summarize(ld_players = n()) %>% filter(ld_team != "NA") %>% 
  full_join(temp_1, temp_2, by = "ld_team")
temp_3 <- select_data %>% 
  filter(ld_gleague == "0") %>% 
  filter(ld_intl == "0") %>% 
  group_by(ld_team) %>% 
  summarize(cap_used = sum(ld_2019, na.rm = TRUE)) %>% 
  mutate(cap_left = 109400000 - cap_used)
ld_hta_team_projections <- full_join(temp_2, temp_3, by = "ld_team") %>% 
  mutate(team_total = avg_fppg * ld_players) %>% 
  arrange(-team_total) %>%
  select(ld_team, ld_players, avg_fppg, team_total, cap_used, cap_left); rm(temp_1, temp_2); rm(temp_3)

temp_1 <- select_data %>% 
  filter(ld_gleague == "0") %>% 
  filter(ld_intl == "0") %>%  
  group_by(trade_comp) %>% summarize(avg_fppg = mean(hta_ld_fpts, na.rm = TRUE)) 
temp_2 <- select_data %>% 
  filter(ld_gleague == "0") %>% 
  filter(ld_intl == "0") %>% 
  group_by(trade_comp) %>% summarize(ld_players = n()) %>% filter(trade_comp != "NA") %>% 
  full_join(temp_1, temp_2, by = "trade_comp")
temp_3 <- select_data %>% 
  filter(ld_gleague == "0") %>% 
  filter(ld_intl == "0") %>% 
  group_by(trade_comp) %>% 
  summarize(cap_used = sum(ld_2019, na.rm = TRUE)) %>% 
  mutate(cap_left = 109400000 - cap_used)
ld_hta_team_posttrade <- full_join(temp_2, temp_3, by = "trade_comp") %>% 
  mutate(team_total = avg_fppg * ld_players) %>% 
  arrange(-team_total) %>%
  select(trade_comp, ld_players, avg_fppg, team_total, cap_used, cap_left); rm(temp_1, temp_2); rm(temp_3)

ld_hta_team_projections; ld_hta_team_posttrade

ggplot(data=ld_hta_team_projections, 
       aes(x=reorder(ld_team, -team_total), y=team_total, fill=ld_team)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  theme_bw() +  theme(axis.title.x=element_blank(), axis.title.y=element_blank()) +
  geom_text(aes(label = ld_players), size = 5, colour="white", fontface="bold", hjust = 0.4, vjust = 3) +
  labs(title = "Legacy Dynasty Rankings - Projected Team Points Per Week (Based on 2018 Stats)", 
       fill = "LD Team") +
  scale_fill_manual(values=c("#C8102E", "#061922", "#008348", "#00788C", "#ce1141", 
                             "#860038", "#007dc5", "#0E2240", "#C8102E", "#1D428A",
                             "#ce1141", "#ffc633", "#1D428A", "#552582", "#5D76A9", 
                             "#98002e", "#00471b", "#78be20", "#b6995a", "#F58426",
                             "#EF3B24", "#007dc5", "#006bb6", "#e56020", "#000000", 
                             "#724c9f", "#bac3c9", "#ce1141", "#002B5C", "#002b5c")) 

ggplot(data=ld_hta_team_posttrade, 
       aes(x=reorder(trade_comp, -team_total), y=team_total, fill=trade_comp)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  theme_bw() +  theme(axis.title.x=element_blank(), axis.title.y=element_blank()) +
  geom_text(aes(label = ld_players), size = 5, colour="white", fontface="bold", hjust = 0.4, vjust = 3) +
  labs(title = "Legacy Dynasty Rankings - Projected Team Points Per Week (Based on 2018 Stats)", 
       fill = "LD Team") +
  scale_fill_manual(values=c("#C8102E", "#061922", "#008348", "#00788C", "#ce1141", 
                             "#860038", "#007dc5", "#0E2240", "#C8102E", "#1D428A",
                             "#ce1141", "#ffc633", "#1D428A", "#552582", "#5D76A9", 
                             "#98002e", "#00471b", "#78be20", "#b6995a", "#F58426",
                             "#EF3B24", "#007dc5", "#006bb6", "#e56020", "#000000", 
                             "#724c9f", "#bac3c9", "#ce1141", "#002B5C", "#002b5c"))

ggplot(data=ld_hta_team_projections, aes(x=reorder(ld_team, -avg_fppg), y=avg_fppg, fill=ld_team)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  theme_bw() + theme(axis.title.x=element_blank(), axis.title.y=element_blank()) +
  geom_text(aes(label = ld_players), size = 3, colour="white", fontface="bold", hjust = 0.4, vjust = 3) +
  labs(title = "Legacy Dynasty Rankings - Avg Fantasy Points Per Player (Based on 2018 Stats)", 
       fill = "LD Team") +
  scale_fill_manual(values=c("#C8102E", "#061922", "#008348", "#00788C", "#ce1141", 
                             "#860038", "#007dc5", "#0E2240", "#C8102E", "#1D428A",
                             "#ce1141", "#ffc633", "#1D428A", "#552582", "#5D76A9", 
                             "#98002e", "#00471b", "#78be20", "#b6995a", "#F58426",
                             "#EF3B24", "#007dc5", "#006bb6", "#e56020", "#000000", 
                             "#724c9f", "#bac3c9", "#ce1141", "#002B5C", "#002b5c"))

ggplot(data=ld_hta_team_posttrade, aes(x=reorder(trade_comp, -avg_fppg), y=avg_fppg, fill=trade_comp)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  theme_bw() + theme(axis.title.x=element_blank(), axis.title.y=element_blank()) +
  geom_text(aes(label = ld_players), size = 3, colour="white", fontface="bold", hjust = 0.4, vjust = 3) +
  labs(title = "Legacy Dynasty Rankings - Avg Fantasy Points Per Player (Based on 2018 Stats)", 
       fill = "LD Team") +
  scale_fill_manual(values=c("#C8102E", "#061922", "#008348", "#00788C", "#ce1141", 
                             "#860038", "#007dc5", "#0E2240", "#C8102E", "#1D428A",
                             "#ce1141", "#ffc633", "#1D428A", "#552582", "#5D76A9", 
                             "#98002e", "#00471b", "#78be20", "#b6995a", "#F58426",
                             "#EF3B24", "#007dc5", "#006bb6", "#e56020", "#000000", 
                             "#724c9f", "#bac3c9", "#ce1141", "#002B5C", "#002b5c"))

```

Post-Trade Comparison Tool HashTag Alt

```{r comparing team projections before and after trade using ht, fig.width=11, fig.height=6, warning=FALSE}
temp_1 <- select_data %>% 
  filter(ld_gleague == "0") %>% 
  filter(ld_intl == "0") %>%  
  group_by(ld_team) %>% summarize(avg_fppg = mean(ht_ld_fpts, na.rm = TRUE)) 
temp_2 <- select_data %>% 
  filter(ld_gleague == "0") %>% 
  filter(ld_intl == "0") %>% 
  group_by(ld_team) %>% summarize(ld_players = n()) %>% filter(ld_team != "NA") %>% 
  full_join(temp_1, temp_2, by = "ld_team")
temp_3 <- select_data %>% 
  filter(ld_gleague == "0") %>% 
  filter(ld_intl == "0") %>% 
  group_by(ld_team) %>% 
  summarize(cap_used = sum(ld_2019, na.rm = TRUE)) %>% 
  mutate(cap_left = 109400000 - cap_used)
ld_team_projections <- full_join(temp_2, temp_3, by = "ld_team") %>% 
  mutate(team_total = avg_fppg * ld_players) %>% 
  arrange(-team_total) %>%
  select(ld_team, ld_players, avg_fppg, team_total, cap_used, cap_left); rm(temp_1, temp_2); rm(temp_3)

temp_1 <- select_data %>% 
  filter(ld_gleague == "0") %>% 
  filter(ld_intl == "0") %>%  
  group_by(trade_comp) %>% summarize(avg_fppg = mean(ht_ld_fpts, na.rm = TRUE)) 
temp_2 <- select_data %>% 
  filter(ld_gleague == "0") %>% 
  filter(ld_intl == "0") %>% 
  group_by(trade_comp) %>% summarize(ld_players = n()) %>% filter(trade_comp != "NA") %>% 
  full_join(temp_1, temp_2, by = "trade_comp")
temp_3 <- select_data %>% 
  filter(ld_gleague == "0") %>% 
  filter(ld_intl == "0") %>% 
  group_by(trade_comp) %>% 
  summarize(cap_used = sum(ld_2019, na.rm = TRUE)) %>% 
  mutate(cap_left = 109400000 - cap_used)
ld_ht_team_posttrade <- full_join(temp_2, temp_3, by = "trade_comp") %>% 
  mutate(team_total = avg_fppg * ld_players) %>% 
  arrange(-team_total) %>%
  select(trade_comp, ld_players, avg_fppg, team_total, cap_used, cap_left); rm(temp_1, temp_2); rm(temp_3)

#ld_ht_team_projections; ld_ht_team_posttrade

ggplot(data=ld_team_projections, 
       aes(x=reorder(ld_team, -team_total), y=team_total, fill=ld_team)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  theme_bw() +  theme(axis.title.x=element_blank(), axis.title.y=element_blank()) +
  geom_text(aes(label = ld_players), size = 3, colour="white", fontface="bold", hjust = 0.4, vjust = 3) +
  labs(title = "Legacy Dynasty Rankings - Projected Team Points Per Week (Based on 2018 Stats)", 
       fill = "LD Team") +
  scale_fill_manual(values=c("#C8102E", "#061922", "#008348", "#00788C", "#ce1141", 
                             "#860038", "#007dc5", "#0E2240", "#C8102E", "#1D428A",
                             "#ce1141", "#ffc633", "#1D428A", "#552582", "#5D76A9", 
                             "#98002e", "#00471b", "#78be20", "#b6995a", "#F58426",
                             "#EF3B24", "#007dc5", "#006bb6", "#e56020", "#000000", 
                             "#724c9f", "#bac3c9", "#ce1141", "#002B5C", "#002b5c")) 

ggplot(data=ld_ht_team_posttrade, 
       aes(x=reorder(trade_comp, -team_total), y=team_total, fill=trade_comp)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  theme_bw() +  theme(axis.title.x=element_blank(), axis.title.y=element_blank()) +
  geom_text(aes(label = ld_players), size = 3, colour="white", fontface="bold", hjust = 0.4, vjust = 3) +
  labs(title = "Legacy Dynasty Rankings - Projected Team Points Per Week (Based on 2018 Stats)", 
       fill = "LD Team") +
  scale_fill_manual(values=c("#C8102E", "#061922", "#008348", "#00788C", "#ce1141", 
                             "#860038", "#007dc5", "#0E2240", "#C8102E", "#1D428A",
                             "#ce1141", "#ffc633", "#1D428A", "#552582", "#5D76A9", 
                             "#98002e", "#00471b", "#78be20", "#b6995a", "#F58426",
                             "#EF3B24", "#007dc5", "#006bb6", "#e56020", "#000000", 
                             "#724c9f", "#bac3c9", "#ce1141", "#002B5C", "#002b5c"))

ggplot(data=ld_hta_team_projections, aes(x=reorder(ld_team, -avg_fppg), y=avg_fppg, fill=ld_team)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  theme_bw() + theme(axis.title.x=element_blank(), axis.title.y=element_blank()) +
  geom_text(aes(label = ld_players), size = 3, colour="white", fontface="bold", hjust = 0.4, vjust = 3) +
  labs(title = "Legacy Dynasty Rankings - Avg Fantasy Points Per Player (Based on 2018 Stats)", 
       fill = "LD Team") +
  scale_fill_manual(values=c("#C8102E", "#061922", "#008348", "#00788C", "#ce1141", 
                             "#860038", "#007dc5", "#0E2240", "#C8102E", "#1D428A",
                             "#ce1141", "#ffc633", "#1D428A", "#552582", "#5D76A9", 
                             "#98002e", "#00471b", "#78be20", "#b6995a", "#F58426",
                             "#EF3B24", "#007dc5", "#006bb6", "#e56020", "#000000", 
                             "#724c9f", "#bac3c9", "#ce1141", "#002B5C", "#002b5c"))

ggplot(data=ld_hta_team_posttrade, aes(x=reorder(trade_comp, -avg_fppg), y=avg_fppg, fill=trade_comp)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  theme_bw() + theme(axis.title.x=element_blank(), axis.title.y=element_blank()) +
  geom_text(aes(label = ld_players), size = 3, colour="white", fontface="bold", hjust = 0.4, vjust = 3) +
  labs(title = "Legacy Dyntasy Rankings - Avg Fantasy Points Per Player (Based on 2018 Stats)", 
       fill = "LD Team") +
  scale_fill_manual(values=c("#C8102E", "#061922", "#008348", "#00788C", "#ce1141", 
                             "#860038", "#007dc5", "#0E2240", "#C8102E", "#1D428A",
                             "#ce1141", "#ffc633", "#1D428A", "#552582", "#5D76A9", 
                             "#98002e", "#00471b", "#78be20", "#b6995a", "#F58426",
                             "#EF3B24", "#007dc5", "#006bb6", "#e56020", "#000000", 
                             "#724c9f", "#bac3c9", "#ce1141", "#002B5C", "#002b5c"))

```

## Projecting Team Totals with Scheduling 

```{r}

select_data$ht_ld_fpts + nba



```









