---
title: "The Invitational Fantasy Tools"
author: "Brandon L. Kramer"
date: "9/2/2019"
output: html_document
---

This file contains the following materials for Legacy Dynasty NBA fantasy points league 

* Concatenation of Basketball Reference (2018), Hashtag (2019), and Hashtag Alt (2019) Projections
* Overall Stats and Projections
* Team Projections
* Team Players Quick Comparisons 
* Post-Trade Comparison Tool 

```{r pull packages and projection data}
#install.packages("tidyverse"); install.packages("googlesheets")
rm(list = ls())
for (pkg in c("googlesheets", "tidyverse", "fmsb", "plotly", "radarchart")) {library(pkg, character.only = TRUE)}

setwd("C:/Users/bkram/CloudStation/NBA/data")
inseason <- read_csv("nba_fantasy_data - invitational_inseason.csv")
invitational_rosters <- read_csv("nba_fantasy_data - the_invitational.csv")

invitational_rosters$player <- invitational_rosters$player %>% 
  str_replace_all(c('Á' = 'A', 'ā' = 'a', 'á' = 'a', 'č' = 'c', 'ć' = 'c', 'è' = 'e', 
                    'é' = 'e', 'ê' = 'e', 'ić' = 'ic', 'ö' = 'o', 'ó' = 'o', 'Š' = 'S', 
                    'š' = 's', 'ū' = 'u', 'ý' = 'y', 'Ž' = 'Z', 'ž' = 'z', 
                    'Élie' = 'Elie','P.J.' = 'PJ','C.J.' = 'CJ', 'R.J.' = 'RJ', 'T.J.' = 'TJ', 
                    'D.J.' = 'DJ', 'J.J.' = 'JJ', 'Dončić' = 'Doncic', 'Louis' = 'Lou', 'Edrice' = 'Bam', 
                    'Waller-Prince' = 'Prince', "O.G." = "OG", "Demarre" = "DeMarre",
                    'Jaren Jackson' = 'Jaren Jackson Jr.','Kelly Oubre' = 'Kelly Oubre Jr.', 
                    'Marvin Bagley' = 'Marvin Bagley III', 'Otto Porter' = 'Otto Porter Jr.', 
                    'Wendell Carter' = 'Wendell Carter Jr.', 'Larry Nance' = 'Larry Nance Jr.',
                    'Walt Lemon' = 'Walt Lemon Jr.', 'Dennis Schröder' = 'Dennis Schroder', 
                    'Tim Hardaway' = 'Tim Hardaway Jr.'))

inseason$player <- inseason$Player %>% 
  str_replace_all(c('Á' = 'A', 'ā' = 'a', 'á' = 'a', 'č' = 'c', 'ć' = 'c', 'è' = 'e', 
                    'é' = 'e', 'ê' = 'e', 'ić' = 'ic', 'ö' = 'o', 'ó' = 'o', 'Š' = 'S', 
                    'š' = 's', 'ū' = 'u', 'ý' = 'y', 'Ž' = 'Z', 'ž' = 'z', 
                    'Élie' = 'Elie','P.J.' = 'PJ','C.J.' = 'CJ', 'R.J.' = 'RJ', 'T.J.' = 'TJ', 
                    'D.J.' = 'DJ', 'J.J.' = 'JJ', 'Dončić' = 'Doncic', 'Louis' = 'Lou', 'Edrice' = 'Bam', 
                    'Waller-Prince' = 'Prince', "O.G." = "OG", "Demarre" = "DeMarre",
                    'Jaren Jackson' = 'Jaren Jackson Jr.','Kelly Oubre' = 'Kelly Oubre Jr.', 
                    'Marvin Bagley' = 'Marvin Bagley III', 'Otto Porter' = 'Otto Porter Jr.', 
                    'Wendell Carter' = 'Wendell Carter Jr.', 'Larry Nance' = 'Larry Nance Jr.',
                    'Walt Lemon' = 'Walt Lemon Jr.', 'Dennis Schröder' = 'Dennis Schroder', 
                    'Tim Hardaway' = 'Tim Hardaway Jr.')) 
inseason <- inseason %>% select(-Player) %>% select(player, everything())


select_data <- invitational_rosters %>% 
  full_join(inseason, by = "player") %>% 
  mutate(ppg = PTS/GP, 
         rpg = (OREB + DREB) / GP,
         apg = AST / GP, 
         spg = ST / GP, 
         bpg = BLK / GP, 
         threes = `3PTM` / GP,
         tpg = TO / GP, 
         ftp = FTM / FTA, 
         fgp = FGM / FGA ) %>% 
  rename(position = Position) %>% 
  select(player, inv_team, inv_abbreviated, ppg, rpg, apg, spg, bpg, threes, tpg, ftp, fgp, FGM, FGA, FTM, FTA)  

rm(combined_data, invitational_rosters, inseason)
```


```{r, looking at projections by cat in bbr stats}
select_data %>% 
  arrange(-apg)
```



# invitational conversions 

```{r}
inv_projections <- select_data %>% 
  group_by(inv_abbreviated) %>% 
  filter(inv_abbreviated != "") %>% 
  summarize(team_pts = sum(ppg, na.rm = TRUE),
            team_rebs = sum(rpg, na.rm = TRUE),
            team_asts = sum(apg, na.rm = TRUE),
            team_stls = sum(spg, na.rm = TRUE),
            team_blks = sum(bpg, na.rm = TRUE),
            team_tovs = sum(tpg, na.rm = TRUE),
            team_threes = sum(threes, na.rm = TRUE),
            team_fgp = (sum(FGM, na.rm = TRUE) / sum(FGA, na.rm = TRUE)),  
            team_ftp = (sum(FTM, na.rm = TRUE) / sum(FTA, na.rm = TRUE)))
            
            

```

```{r hashtag rankings graphed, fig.width=11, fig.height=6, warning=FALSE}
# points 
ggplot(data=inv_projections, aes(x=reorder(inv_abbreviated, -team_pts), y=team_pts, fill=inv_abbreviated)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  geom_text(aes(label = round(team_pts)), size = 2.3, colour="black", fontface="bold", hjust = 0.5, vjust = 3) +
  theme_bw() +
  theme(axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title = "The Invitational Rankings - Projected Team Points (Based on 2019 Hashtag)", fill = "Team")

# rebounds 
ggplot(data=inv_projections, aes(x=reorder(inv_abbreviated, -team_rebs), y=team_rebs, fill=inv_abbreviated)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  geom_text(aes(label = round(team_rebs)), size = 2.3, colour="black", fontface="bold", hjust = 0.5, vjust = 3) +
  theme_bw() +
  theme(axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title = "The Invitational Rankings - Projected Team Rebounds (Based on 2019 Hashtag)", fill = "Team")

# assists 
ggplot(data=inv_projections, aes(x=reorder(inv_abbreviated, -team_asts), y=team_asts, fill=inv_abbreviated)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  geom_text(aes(label = round(team_asts)), size = 2.3, colour="black", fontface="bold", hjust = 0.5, vjust = 3) +
  theme_bw() +
  theme(axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title = "The Invitational Rankings - Projected Team Assists (Based on 2019 Hashtag)", fill = "Team")

# steals 
ggplot(data=inv_projections, aes(x=reorder(inv_abbreviated, -team_stls), y=team_stls, fill=inv_abbreviated)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  geom_text(aes(label = round(team_stls)), size = 2.3, colour="black", fontface="bold", hjust = 0.5, vjust = 3) +
  theme_bw() +
  theme(axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title = "The Invitational Rankings - Projected Team Steals (Based on 2019 Hashtag)", fill = "Team")

# blocks 
ggplot(data=inv_projections, aes(x=reorder(inv_abbreviated, -team_blks), y=team_blks, fill=inv_abbreviated)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  geom_text(aes(label = round(team_blks)), size = 2.3, colour="black", fontface="bold", hjust = 0.5, vjust = 3) +
  theme_bw() +
  theme(axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title = "The Invitational Rankings - Projected Team Blocks (Based on 2019 Hashtag)", fill = "Team")

# turnovers 
ggplot(data=inv_projections, aes(x=reorder(inv_abbreviated, team_tovs), y=team_tovs, fill=inv_abbreviated)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  geom_text(aes(label = round(team_tovs)), size = 2.3, colour="black", fontface="bold", hjust = 0.5, vjust = 3) +
  theme_bw() +
  theme(axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title = "The Invitational Rankings - Projected Team Turnovers (Based on 2019 Hashtag)", fill = "Team")

# threes 
ggplot(data=inv_projections, aes(x=reorder(inv_abbreviated, -team_threes), y=team_threes, fill=inv_abbreviated)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  geom_text(aes(label = round(team_threes)), size = 2.3, colour="black", fontface="bold", hjust = 0.5, vjust = 3) +
  theme_bw() +
  theme(axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title = "The Invitational Rankings - Projected Team Threes (Based on 2019 Hashtag)", fill = "Team")

# fgp 
ggplot(data=inv_projections, aes(x=reorder(inv_abbreviated, -team_fgp), y=team_fgp, fill=inv_abbreviated)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  geom_text(aes(label = round(team_fgp,digits=2)), size = 2.3, colour="black", fontface="bold", hjust = 0.5, vjust = 3) +
  theme_bw() +
  theme(axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title = "The Invitational Rankings - Projected Team FG% (Based on 2019 Hashtag)", fill = "Team")

# ftp 
ggplot(data=inv_projections, aes(x=reorder(inv_abbreviated, -team_ftp), y=team_ftp, fill=inv_abbreviated)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  geom_text(aes(label = round(team_ftp,digits=2)), size = 2.3, colour="black", fontface="bold", hjust = 0.5, vjust = 3) +
  theme_bw() +
  theme(axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title = "The Invitational Rankings - Projected Team FG% (Based on 2019 Hashtag)", fill = "Team")

```


```{r hashtag alt rankings graphed, fig.width=11, fig.height=6, warning=FALSE}
# points 
ggplot(data=inv_projections, aes(x=reorder(inv_abbreviated, -team_pts), y=team_pts, fill=inv_abbreviated)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  geom_text(aes(label = team_pts), size = 2.3, colour="black", fontface="bold", hjust = 0.5, vjust = 3) +
  theme_bw() +
  theme(axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title = "The Invitational Rankings - Projected Team Points (Based on 2019 Hashtag Alt)", fill = "Team")

# rebounds 
ggplot(data=inv_projections, aes(x=reorder(inv_abbreviated, -team_rebs), y=team_rebs, fill=inv_abbreviated)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  geom_text(aes(label = team_rebs), size = 2.3, colour="black", fontface="bold", hjust = 0.5, vjust = 3) +
  theme_bw() +
  theme(axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title = "The Invitational Rankings - Projected Team Rebounds (Based on 2019 Hashtag Alt)", fill = "Team")

# assists 
ggplot(data=inv_projections, aes(x=reorder(inv_abbreviated, -team_asts), y=team_asts, fill=inv_abbreviated)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  geom_text(aes(label = team_asts), size = 2.3, colour="black", fontface="bold", hjust = 0.5, vjust = 3) +
  theme_bw() +
  theme(axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title = "The Invitational Rankings - Projected Team Assists (Based on 2019 Hashtag Alt)", fill = "Team")

# steals 
ggplot(data=inv_projections, aes(x=reorder(inv_abbreviated, -team_stls), y=team_stls, fill=inv_abbreviated)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  geom_text(aes(label = team_stls), size = 2.3, colour="black", fontface="bold", hjust = 0.5, vjust = 3) +
  theme_bw() +
  theme(axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title = "The Invitational Rankings - Projected Team Steals (Based on 2019 Hashtag Alt)", fill = "Team")

# blocks 
ggplot(data=inv_projections, aes(x=reorder(inv_abbreviated, -team_blks), y=team_blks, fill=inv_abbreviated)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  geom_text(aes(label = team_blks), size = 2.3, colour="black", fontface="bold", hjust = 0.5, vjust = 3) +
  theme_bw() +
  theme(axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title = "The Invitational Rankings - Projected Team Blocks (Based on 2019 Hashtag Alt)", fill = "Team")

# turnovers 
ggplot(data=inv_projections, aes(x=reorder(inv_abbreviated, team_tovs), y=team_tovs, fill=inv_abbreviated)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  geom_text(aes(label = team_tovs), size = 2.3, colour="black", fontface="bold", hjust = 0.5, vjust = 3) +
  theme_bw() +
  theme(axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title = "The Invitational Rankings - Projected Team Turnovers (Based on 2019 Hashtag Alt)", fill = "Team")

# threes 
ggplot(data=inv_projections, aes(x=reorder(inv_abbreviated, -team_threes), y=team_threes, fill=inv_abbreviated)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  geom_text(aes(label = team_threes), size = 2.3, colour="black", fontface="bold", hjust = 0.5, vjust = 3) +
  theme_bw() +
  theme(axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title = "The Invitational Rankings - Projected Team Threes (Based on 2019 Hashtag Alt)", fill = "Team")

# fgp 
ggplot(data=inv_projections, aes(x=reorder(inv_abbreviated, -team_fgp), y=team_fgp, fill=inv_abbreviated)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  geom_text(aes(label = round(team_fgp,digits=2)), size = 2.3, colour="black", fontface="bold", hjust = 0.5, vjust = 3) +
  theme_bw() +
  theme(axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title = "The Invitational Rankings - Projected Team FG% (Based on 2019 Hashtag Alt)", fill = "Team")

# ftp 
ggplot(data=inv_projections, aes(x=reorder(inv_abbreviated, -team_ftp), y=team_ftp, fill=inv_abbreviated)) +
  geom_bar(stat="identity", width=0.6, colour="black") +
  geom_text(aes(label = round(team_ftp,digits=2)), size = 2.3, colour="black", fontface="bold", hjust = 0.5, vjust = 3) +
  theme_bw() +
  theme(axis.title.x=element_blank(), 
        axis.title.y=element_blank()) +
  labs(title = "The Invitational Rankings - Projected Team FG% (Based on 2019 Hashtag Alt)", fill = "Team")

```


```{r looking at specific team's player projections}
select_data %>% 
  filter(inv_abbreviated == "TREE") %>% 
  select(player, age, pts:trade_comp) %>% 
  arrange(-pts)
  
```

# spider charts of teams 

```{r list of team names}
inv_projections$inv_abbreviated

```

# two-team spider plots 

```{r interactive spider plot, fig.width=8, fig.height=6}

inv_matrix <- inv_projections %>% 
  select(inv_abbreviated, team_pts:team_ftp) %>% 
  filter(inv_abbreviated == "BBB" | inv_abbreviated == "GB" ) %>% 
  mutate(team_pts = team_pts/2, 
         team_stls = team_stls,
         team_blks = team_blks,
         team_threes = team_threes,
         team_fgp = team_fgp*100,
         team_ftp = team_ftp*100) %>% 
  mutate_if(is.numeric, round, digits = 1) %>% 
  rename(points = team_pts, rebounds = team_rebs, assists = team_asts, steals = team_stls,
         blocks = team_blks, turnovers = team_tovs, threes = team_threes, fgp = team_fgp, ftp = team_ftp) %>% 
  column_to_rownames(var = "inv_abbreviated") 

labs <- c("points","rebounds","assists","steals","blocks","turnovers","threes","fg%","ft%")
scores <- as.list(as.data.frame(t(inv_matrix)))
colors <- grDevices::col2rgb(c("#82D4BB","#1789FC"))
chartJSRadar(scores=scores, labs=labs, showToolTipLabel = TRUE, colMatrix = colors)

```

# all team spider plots 

```{r interactive spider plot, fig.width=9.5, fig.height=8}

inv_matrix <- inv_projections %>% 
  select(inv_abbreviated, team_pts:team_ftp) %>% 
  filter(inv_abbreviated == "ALi"  | inv_abbreviated == "BASK" | inv_abbreviated == "BBB"  | inv_abbreviated == "BEET" | 
         inv_abbreviated == "CLAS" | inv_abbreviated == "GB"   | inv_abbreviated == "GMBL" | inv_abbreviated == "HAWK" |
         inv_abbreviated == "HEAT" | inv_abbreviated == "JESI" | inv_abbreviated == "JFOX" | inv_abbreviated == "KANO" |
         inv_abbreviated == "LGR"  | inv_abbreviated == "MLDR" | inv_abbreviated == "NJ15" | inv_abbreviated == "PIP"  | 
         inv_abbreviated == "PP"   | inv_abbreviated == "SERB" | inv_abbreviated == "TREE" | inv_abbreviated == "WOLV" ) %>%   
  mutate(team_pts = team_pts/2, 
         team_asts = team_asts,
         team_stls = team_stls,
         team_blks = team_blks,
         team_threes = team_threes,
         team_tovs = team_tovs,
         team_fgp = team_fgp*100,
         team_ftp = team_ftp*100) %>% 
  mutate_if(is.numeric, round, digits = 1) %>% 
  rename(points = team_pts, rebounds = team_rebs, assists = team_asts, steals = team_stls,
         blocks = team_blks, turnovers = team_tovs, threes = team_threes, fgp = team_fgp, ftp = team_ftp) %>% 
  column_to_rownames(var = "inv_abbreviated") 

labs <- c("points/2","rebounds","assists","steals","blocks","turnovers","threes","fg%","ft%")
scores <- as.list(as.data.frame(t(inv_matrix)))
colors <- grDevices::col2rgb(c('#e6194b', '#3cb44b', '#ffe119', '#4363d8', '#f58231', '#911eb4', '#46f0f0', '#f032e6', '#bcf60c', '#fabebe', '#008080', '#e6beff', '#9a6324', '#fffac8', '#800000', '#aaffc3', '#808000', '#ffd8b1', '#000075', '#808080', '#ffffff', '#000000'))
chartJSRadar(scores=scores, labs=labs, showToolTipLabel = TRUE, colMatrix = colors)

```




